%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sworup Shakya - Frontend Developer Resume
% Version 3.1
% This resume is formatted using a custom 'resume.cls' class file, which is included in the repository.
% To compile this document, ensure 'resume.cls' is in the same directory as this .tex file.
% You can find common versions of this file on Overleaf or other LaTeX template galleries, but the one used here is customized.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style
\usepackage{ragged2e} % For \raggedright in summary
\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins 
\hypersetup{hidelinks} % For clickable links
 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% --- HEADER INFORMATION ---
\name{Sworup Shakya}
\address{+1(224) 527-0688 \\ Elk Grove Village, IL, USA} 
\address{\href{mailto:career@sworup.dev}{career@sworup.dev} \\ \href{https://linkedin.com/in/sworup-shakya}{linkedin.com/in/sworup-shakya} \\ \href{https://github.com/sworup}{github.com/sworup} \\ \href{https://www.sworup.dev}{sworup.dev}}

\begin{document}

%----------------------------------------------------------------------------------------
%   SUMMARY SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Professional Summary}
{\raggedright
Accomplished \textbf{Full-stack Software Engineer} with over 15 years of experience architecting, building, and deploying complex, enterprise-scale systems. Specializing in full-stack \textbf{JavaScript (Node.js, React, Vue.js)}, I have a proven track record of leading teams in modernizing applications, designing robust microservice architectures, and optimizing large-scale ETL pipelines for global platforms. My background includes developing digital asset marketplaces and critical healthcare logistics systems. I am actively seeking challenging contract engagements on a \textit{Corp-to-Corp (C2C)} basis where I can leverage my expertise to deliver scalable and high-quality software solutions.
\par}
\end{rSection}

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}
\begin{tabular}{ @{} >{\bfseries}p{0.22\textwidth} @{\hspace{4ex}} p{0.66\textwidth} }
  Backend & Node.js, Express, REST APIs, GraphQL, PHP \\
  Frontend & JavaScript (ES6+), TypeScript, React, Vue.js, React Native, Redux, Tailwind CSS, Webpack, Vite \\
  Databases & PostgreSQL, MySQL, MongoDB, Redis \\
  Cloud \& DevOps & Docker, CI/CD \\
  Methodologies & Agile/SCRUM, System Design, Component-Driven Development \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Experience}

\textbf{Lead Software Engineer} \hfill Feb 2023 - July 2025 \\
\href{https://uba-solutions.com/}{UBA Solutions Pvt. Ltd.} / \href{https://www.monotype.com/}{Monotype} \hfill \textit{Full-time(Hybrid)}
 \begin{itemize}
    \itemsep -3pt {}
    \item Lead a team with frontend and backend developers and QA, in the design and implementation of high-quality, scalable web applications for \href{https://www.monotype.com/}{Monotype Fonts(MTF)}'s enterprise font management and distribution platform, serving a global user base.
    \item Took ownership of important parts the enterprise side of ETL(Extract, Transform, Load) system of MTF spanning multiple micro-services. The key responsibilities were to make sure the data coming in from various sources such as user upload and PIM (Product Information Management) system were getting to the presentation layer and to other sections such as Asset Delivery System (ADS), Catalog Management System (CMS) etc. correctly.
    \item Engineered a system to automatically sync fonts for clients with tens of thousands of font files onto remote server farms. Integrated multiple micro-services and optimized the process to handle large data volumes efficiently. Stacks included \textbf{Node.js, Micro-services, .NET, MongoDB, RabbitMQ, MySQL}.
    \item Directed a large-scale data integrity initiative, cleaning and migrating millions of ETL records to eliminate data conflicts and ensure reliable data propagation across all consumer-facing services.
    \item Spearheaded a major technical upgrade by migrating 26+ microservices to the latest Node.js LTS version, resolving critical vulnerabilities, modernizing the core backend framework, and improving overall system performance.
    \item Upgraded the definition and format of CSS properties storage in the system to the current industry standard, updating backend and frontend services, ETL and database schemas to ensure compatibility third party services.
    \item Designed and delivered a successful Proof of Concept (PoC) for a zero-trust, microservice-based authentication system using AWS Lambda and .NET Core, which was subsequently adopted and implemented by the company.
    \item Engineered the backend and frontend services for a font tiering feature, enabling the categorization and display of fonts based on complexity and cost within the enterprise platform. Implemented the necessary business logic and data transformations to support this feature. This involved designing RESTful API endpoints, database schema modifications, and creating intuitive UI components to enhance user experience. Stacks included \textbf{Nuxt.js, Node.js, Express, MongoDB}.
    \item Revamped the user interface for the \href{https://fontplatform.monotype.com/}{Monotype Foundry Platform (MFP)} by designing and implementing an expanded site navigation system, fonts upload and consumption interfaces, related fonts management, and a new post-login dashboard. Migrated multiple components from \textbf{Vue 2} to \textbf{Vue 3} and established migration patterns and testing practices for remaining component upgrades. Delivered measurable improvements in UX, application performance, and security, aligning the platform with current industry standards.
    \item Improved frontend application performance by over 80\% by implementing an advanced asset caching strategy with Vite, significantly enhancing the CLS (Cumulative Layout Shift) and LCP (Largest Contentful Paint) scores.
 \end{itemize}
 
\textbf{Senior Software Developer} \hfill Aug 2018 - Feb 2023 \\
\href{https://sussol.net/}{Sustainable Solutions (NZ) Ltd.} \hfill \textit{Full-Time(Onsite)}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Modernized the flagship offline first, sync-able and optimized for android tablets, pharmaceutical logistics mobile application, \href{https://msupply.org.nz/mobile/}{mSupply Mobile}, by leading a full-stack upgrade using \textbf{React Native, Redux, and RealmDB}, enhancing both security and performance.
     \item Developed key components for a custom GraphQL API, \href{https://docs.conforma.nz/docs/about/introduction/}{Conforma}, to support the creation of complex, dynamic forms, improving data accuracy and collection efficiency.
     \item Built multiple standalone companion applications for data collection and reporting using \textbf{React, Redux, MySQL, PostgreSQL, Grafana and Tailwind CSS}, which streamlined data processes and enhanced reporting capabilities.
     \item Maintained and enhanced a customized \textbf{Grafana} fork using \textbf{Go and React}, building custom plugins for advanced data visualization and client-side reporting.
     \item Contributed to flagship desktop application, \href{https://msupply.org.nz/}{mSupply Desktop}, a pharmaceutical logistics platform and supply chain management system, by developing new features and optimizing existing functionalities using database first \textbf{\href{https://us.4d.com/}{4D}} language.
 \end{itemize}

\textbf{Senior Software Developer} \hfill Aug 2015 - Aug 2018 \\
\href{https://www.zimris.com/}{Zimris Technologies} \hfill \textit{Full-Time(Onsite)}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Led a 3-person development team and managed the full project lifecycle for various client-facing web applications. The main task was a full modernization of a name suggestion website and its online forum built using \textbf{Vue.js, PHP (Laravel Lumen) and MySQL}.
     \item Architected and launched "Baby Name Genie," a high-traffic website that successfully handled hundreds of thousands of daily requests, built with Vue.js and a custom, performance-optimized fork of Lumen (Laravel).
     \item Engineered a multi-tenant site generator (CloudCarpenter) using \textbf{JQuery, PHP (Symfony Framework) and MySQL}, enabling clients to dynamically generate and customize their own CMS-based websites from predefined templates.
 \end{itemize}

 \textbf{Early Career Highlights} \hfill 2007 - 2015 
 \begin{itemize}
    \itemsep -3pt {} 
     \item \textbf{Biz Technologies Pvt. Ltd., Senior Software Developer (October 2014 – July 2015)}: Developed full-featured travel booking portals using PHP (CodeIgniter) and JQuery.
     \item \textbf{Wise Yak Solutions Pvt. Ltd., Senior Web Developer (ASP.NET) (July 2013 – September 2014)}: Built custom modules, plugins, and themes for the Orchard CMS platform using \textbf{ASP.NET MVC4, JQuery}.
     \item \textbf{Hitechvalley iNet Pvt. Ltd., Senior Software Developer (October 2011 – June 2013)}: Developed CMS and portal websites using PHP CodeIgniter, CakePHP frameworks and interactive Flash/ActionScript applications.
     \item \textbf{\href{https://grafioffshorenepal.com/news/online-homework-platform-bingel-be/}{Grafi Offshore Nepal}, Senior ActionScript/Flash Developer (January 2010 – September 2011)}: Developed a core game engine and multiple games in ActionScript 3 for a large-scale, gamified e-learning platform called \href{https://www.vanin.be/lager-onderwijs/bingel/}{Bingel.be}.
     \item \textbf{Hitechvalley iNet Pvt. Ltd., Senior Flash/Software Developer (November 2008 – November 2009)}: Developed interactive Flash ActionScript websites and expanded skillset to include PHP, JavaScript, and CMS platforms like WordPress and PyroCMS.
     \item \textbf{Freelance Flash Developer (January 2006 – November 2008)}: Created custom Flash/ActionScript applications and websites for various clients, honing skills in client communication and project management.
 \end{itemize}
 
\end{rSection} 

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Bachelor of Information Technology (BIT)} \textit{CGPA: 3.03} \hfill {2007} \\
\href{https://kist.edu.np/program/bit}{KIST College of Information Technology (KIST-CIT)} \hfill {\textit{Affiliated to \href{https://www.purbanchaluniversity.edu.np/}{Purvanchal University, Nepal.}}} \\
\end{rSection}

%----------------------------------------------------------------------------------------
%   ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------
\begin{rSection}{Additional Information} 
\begin{itemize}
    \itemsep -3pt {}
    \item \textbf{Publications:} Technical Reviewer for "Mastering PHP Design Patterns" by Junade Ali (2016).
    \item \textbf{Languages:} English (Full Professional), Nepali (Native), Hindi (Conversational Proficiency).
\end{itemize}
\end{rSection}

\end{document}
